MinCall --- MinION end2end deep learning basecaller

### 2017-06-30 paper/main.tex
Update

>>>>

During testing we tried ReLu and PrELU~\cite{prelu} with no significat result difference. We also tried different channel numbers, receptive field width and various other hyperparameters during hyperparameter optimization and conclude after enough complexity, that is sufficient layers, all choices were performing similarly.
